Modular transmission line probes for microfluidic nuclear magnetic resonance spectroscopy and imaging

### 2019-03-30 ms5n17-tlp-mn-180216-001.tex
Update ms5n17-tlp-mn-180216-001.tex

\documentclass[preprint,5p]{elsarticle}
\usepackage{graphicx,amssymb,amsmath,amstext,hyperref,graphics,float,eurosym,geometry,lineno,changebar}
%\linenumbers
\biboptions{sort&compress}
\hypersetup{
    colorlinks=true,        % false: boxed links; true: colored links
    linkcolor=black,         % color of internal links (change box color with linkbordercolor)    https://www.sharelatex.com/learn/Hyperlinks
    citecolor=black,        % color of links to bibliography
    filecolor=black,      % color of file links
    urlcolor=black           % color of external links
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In this paper we present a novel modular probe designed for generic
microfluidic-NMR experiments. The design is based on a transmission line
detector~\cite{stripline_jan,gream_2016} using inexpensive
printed circuit board (PCB) technology. A modular design ensures that detectors of
different geometry and size can be easily exchanged.
The NMR detector (including the tuning and matching circuit) is connected to the probe
skeleton through detachable connectors. Modularity of the probe not only allows
fast optimisation of the detector but also facilitates the use of dedicated detectors
for different microfluidic devices on a single probe base.
Once the probe base is in place, additional detectors can be manufactured
within 2-3 days for less than $\sim$200 $\geneuro$.
The probe is optimised for proton detected double resonance, with the
second channel tunable to different nuclei such as $^{13}$C, $^{15}$N, or
$^{31}$P. The probe skeleton is made almost entirely from easily obtainable raw materials
such as aluminium profiles of standard size, with only a small number of
custom-machined parts holding the structure together.
Detailed construction drawings and a complete set of CAD files is
available for download at \url{https://github.com/marcel-utz/modular-microfluidic-probe}.
The planar geometry of the detector accommodates exchangeable microfluidic devices
which can be designed freely for specific experimental requirements as long as the
overall shape of the device is maintained. \fig{fig:rf-device-assembly} shows the microfluidic device and the detector with their relative positioning.

In the remainder of this paper, we discuss the probe design in more detail,
and characterise its performance in terms of sensitivity and resolution.
We also demonstrate its application in microfluidic cell culture,
protein NMR spectroscopy, and micro-imaging.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Probe Design}
\label{sec:probe-design}
%Figure showing modular probe concept; example of probe base with several inserts\newline
%\begin{itemize}
%	\item Philosophy: use cheap materials and prefab Al profiles wherever possible
%	\item Hold it together with a small number of precision-machined parts
%	\item Generic probe base design that can accommodate a variety of inserts
%	\item Insert: PCB that accommodates both tuning/matching circuitry for up to two channels and the transmission line probe itself
%	\item Tuning and matching capacitors for each channel are part of the probe base
%	\item Connection using standard coaxial RF connectors (SMP)
%	\item Microfluidic chip design; outline
%	\item Design/explosion drawings
%	\item Circuit design for double resonance
%	\item Transmission line connection between tuning/matching of 1H channel and resonator (Smith chart argument)
%	\item 38 mm bore (Bruker NB) and 45 mm bore (Varian/Agilent NB)
%\end{itemize}
\cbstart
\begin{figure}
\centering
\includegraphics[width=.8\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-190205-rf-device-assembly.png}
\caption{Drawings of the detector assembly and the microfluidic device (1). A: front view; B: exploded view. Spacer (4) ensures the alignment of the sample chamber with the constrictions on the PCB planes. In A, PCB plane 5 is hidden to show the orientation of 1 with respect to PCB plane 3. Thickness of each of the PCB planes is 1.52 mm and the copper layers on the PCBs is 35 $\mu$m. Both the microfluidic device and the spacer are made from PMMA and have thickness of 0.9 mm and 1 mm respectively.}
\label{fig:rf-device-assembly}
\end{figure}
\cbend
%\begin{figure}
%\centering
%\includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181218-probe.png}
%\caption{The probe with and without sleeve.}
%\label{fig:probe}
%\end{figure}
The probe assembly design is based on readily and easily available materials and parts
with minimal need for customised fabrication.
All mechanical and electronic components are readily available from commercial sources,
with the exception of a small number of precision-machined parts which are used
to hold the assembly together. These can be ordered from commercial prototyping
manufacturers or machined in-house if mechanical workshop facilities are available.

\begin{figure}
\centering
\includegraphics[width=.8\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-Probe-explode.png}
\caption{Exploded view of the probe design (left) and assembled probe (right).
Probe base (blue) and scaffold assembly (green) with TMPCB (brown, 7) provides a
generic mounting point for the NMR detector assembly (red).
A microfluidic device (1) can be inserted from the top of the probe.
The device is held in place by a spacer (4) between the detector planes (3 and 5)
ensuring alignment of the sample chamber with the sensitive area on the PCB planes.
The modular NMR detector is made up of parts 3,4 and, 5 and is
connected to the TMPCB (7) through standard coaxial (SMP) connectors.
The scaffold assembly is made up of aluminium tubes (11), scaffold support disks (9)
and, auxiliary support disks (12).}
\label{fig:probe-explode}
\end{figure}

@@

The scaffold assembly is made up of two hollow aluminium tubes (11) held together with
precision machined parts at both ends (scaffold support disks (9)).\cbstart
The semi-rigid cables (RG 402, 50~$\Omega$) are  threaded through these hollow aluminium tubes
to reach the detector assembly.\cbend
Auxiliary support disks (12) provide additional rigidity for the scaffold assembly.
In our case, these were laser cut from 5~mm thick poly(methyl methacrylate) (PMMA) sheets,
but they may also be made by conventional machining.
A tuning and matching PCB (TMPCB, 7) is held in place on the top of the probe skeleton by
the detector support rods (8), with the semi-rigid coaxial cables providing
additional support.
The TMPCB is permanently fixed to the probe base, and serves as attachment point
for the exchangeable detector assembly. \cbstart It also provides
trimmer capacitors (6) for secondary tuning and matching of the detector.\cbend
 The detector assembly is connected to the TMPCB through a pair of
low-loss SMP connectors (14 in \fig{fig:ProbePhoto}). \cbstart SMP Connector Receptacle Male Pin ($J_3$ and $J_4$ in \fig{fig:circuit}) is soldered on the TMPCB and SMP Connector Jack Male Pin is soldered on the PCB plane 3 ($J_1$ and $J_2$ in \fig{fig:circuit}). The TMPCB and 3 are connected by a coaxial connector SMP plug adapter.\cbend
While each detector assembly is roughly
tuned and matched with fixed circuit elements soldered onto it,
the adjustable capacitors on the TMPCB are used for
fine tuning and matching
at the magnet through tuning rods (10) which reach all the way to the probe base.

The base, the scaffold assembly and the tuning and matching PCB all have a free circular
axial bore providing access from the bottom of the probe, which can be used for
temperature and environmental control and/or fluidic connections to the sample as
needed. The detector assembly is made up of two PCBs (3 and 5) and a spacer (4) between them. \cbstart The spacer is made from a 1 mm thick PMMA sheet.\cbend  The detector used here is based on a planar transmission line geometry as described elsewhere~\cite{gream_2016,stripline_jan}; other structures such as spiral
coils and Helmholtz pairs are also possible, and can easily be realised on a PCB.
The transmission line detector consists of a pair of copper
planes, each with a constriction at the centre.  This geometry gives rise to an
electromagnetic eigenmode with a strong anti-node of the magnetic field between
the two planes at the site of the constriction. This concentrates the rf field
and the detection sensitivity
onto the sample area.
The shape and size of the copper structures have been chosen such as to produce
an eigenfrequency of this mode around 630~MHz. The PCBs have been designed with
solder points at the back side for chip capacitors; these can be used to tune the
resonance down to the desired proton Larmor frequency (500 or 600~MHz in the present case).
Both the PCBs (3 and 5) also carry circuitry for channel separation and primary
matching of the detector. A copper or brass auxiliary disk (2) holds the PCBs
together at the top, and forms the top end of the probe assembly.
The probe sheath (not shown in~\fig{fig:probe-explode}) is fixed to the auxiliary disk (2)
and the scaffold assembly with screws.
An exchangeable microfluidic device (1) can be inserted from the top of the detector.
Microfluidic devices can be used as passive sample holders, filled before putting them
into the probe,
or the device can be actively perfused and operated in-situ.\cbstart The device inlet and outlet are sealed by an optical adhesive film (MicroAmp, AB Applied Biosystems)
when using the device as passive sample holder.\cbend
 The microfluidic device is held in place by the spacer
between the two PCB planes coinciding the sample chamber with the constriction on the
detector.  The 45-degree edges of the device outline help with precise and reliable
alignment.
Since the detector assembly is attached to the probe base through SMP
connectors, it can easily be exchanged.
Using standard PCB processes to manufacture the detector provides great flexibility
to optimise detector performance for different applications, including different
microfluidic sample sizes, and different combinations of target nuclei.

\begin{figure}
\centering
\includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-both-detectors.png}
\caption{Dual channel probes with (A) and without (B) modular RF insert (13) for X channel.
O.D. of A is 44.45 mm and B is 38 mm. Circuit elements of X channel are integrated on the
PCB in B making it compact. Detachable SMP connectors (14) are used to
connect the RF insert (13) and the detector assembly.}
\label{fig:ProbePhoto}
\end{figure}
\fig{fig:ProbePhoto} shows two different versions of the probe with and without the RF insert (13)
for the X channel. In (A) the X channel can be tuned to different nuclei by exchanging 13.
However, in (B) the circuitry of the RF insert (13) is integrated on the PCB plane (5),
making the design more compact.
 Probe (A) is compatible with a Varian 600 Premium shielded 14.1 T magnet, with an outer diameter (O.D.) of 44.45 mm including the sheath. Probe (B), with an
O.D. of 38 mm including the sheath, is designed to fit inside a
Bruker narrow bore shim stack.
Probe (B) also fits inside a Bruker micro-imaging gradient unit. Naturally, B can also be used with
wide bore magnets with spacers or gradient stack to keep the probe centred.

Microfluidic devices are made from inexpensive PMMA sheets by laser cutting and
thermal bonding, as described in detail elsewhere \cite{yilmaz_bonding}. \cbstart Magnetic susceptibility value of PMMA and other materials in given in table~\ref{tab:susceptibility}\cbend
Briefly, the devices consist of a 0.5~mm thick middle layer between a  top and
bottom layer of 0.2~mm thickness each. The sample chamber and fluidic network
are cut into the middle layer. The fluidic network on the device can be designed
freely as long as the overall shape of the device is preserved, and the location
of the sample chamber is maintained. The volume of the sample chamber is 2.5~$\mu$l which can be increased or decreased according to the experimental requirements. \cbstart \fig{fig:device} shows various microfluidic devices.\cbend
\cbstart
\begin{table}[h]
\centering
\caption{Magnetic susceptibility values of the materials used in the probe\cite{wapler-2014,schenck-1996}}
\label{tab:susceptibility}
\begin{tabular}{||p{.3\linewidth}|p{.3\linewidth}||}
\hline
Material   & $\chi$/ppm	\\
\hline
PMMA		&-9.054	\\
Copper	&-9.63	\\
FR4	&-3.743		\\
Aluminium	&20.7	\\
\hline
\end{tabular}
\end{table}
\cbend
\cbstart
\begin{figure}
\centering
\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-devices.png}
\caption{Microfluidic devices for different applications compatible with the current setup.
From left: Devices for perfusion of tissue slice on a chip, peristaltic pumping to induce flow,
hydrogenation on a chip, droplet generator, simple design to fill the sample chamber and,
to grow cells on the device.}
\label{fig:device}
\end{figure}
\cbend

@@

\caption{Circuit diagram of the double resonance probe. The background colour relates the different circuit elements on different PCBs. The back side of the PCB plane 5 and the front side of the PCB plane 3 is shown in horizontal orientation. The front side of the TMPCB 7 is shown in vertical orientation. Trimmer capacitor $C_6$ is placed on the back side of PCB plane 5. The copper layer is shown in brown and the solder pads to place the circuit elements are shown in off-white. An insulating solder mask layer over the copper layer prevents accidental short-circuiting.

@@

\cbstart
\begin{figure} \centering
\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/pcb-fieldmap-colorbar.png}
\caption{B\textsubscript{0} field map of the sample chamber for FR4 (A) and
Rogers RO3035 (B) PCB material acquired at 11.7 T. Both the field maps were constructed from 2
gradient echo images acquired on a chip filled with 130 mM sodium acetate
dissolved in H\textsubscript{2}O through same parameters and pulse sequence.}
\label{fig:field map}
\end{figure}
\cbend
\cbdelete
The RF field at proton frequency shows excellent homogeneity, with a
810$^{\circ}$/90$^{\circ}$ ratio of more than 90\% measured from $^1$H nutation at 600~MHz shown in~\fig{fig:1H-nutation}. The
probe generates 100~kHz nutation frequency from 100~W input power both at
600~MHz and 500~MHz, corresponding to RF field efficiency ($B_{1}/\sqrt{power}$)
of 10 kHz/$\sqrt{W}$. The detector geometry has been optimised for a sample
volume of 5~$\mu$l. It compares reasonably well to the value of 22
kHz/$\sqrt{W}$ that has been reported by Finch et al.~\cite{gream_2016} for
single-frequency detector of half this size at a Larmor frequency of 300~MHz.
For X channel, 100~W of input power produces nutation frequencies of 6 kHz for
$^{15}$N and 14 kHz for $^{13}$C. No signs of arcing were obseved at this power
level for pulses up to 1~ms duration.

@@

\begin{figure}
\centering
\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/media-180125-005-bigger-font.png}
\caption{Spectrum of culture growth media recorded in 256 scans with water presaturation. The total experimental time was 20 min for 2.5 $\mu$l sample volume.}
\label{fig:media-spec}
\end{figure}
\cbdelete
\fig{fig:lineshape} shows the proton spectrum of sodium acetate. The inset shows an expanded view of the base of the acetate peak. Carbon satellites can be seen well above the noise level. The orange curve
corresponds to a Lorentzian lineshape with full width at half maximum of 3.35
Hz, corresponding to 0.0056 ppm. This is very similar to the resolution reported
by Finch et al. at 300~MHz. While the residual cause of broadening is still
under investigation, we have reason to suspect imperfections in the fabrications
of the PMMA microfluidic devices to play a major role. Efforts to mitigate these
and to achieve more highly resolved proton spectra are currently underway in our
laboratory and will be reported at a later occasion.  The limit of detection
$nLOD_{\omega}=\frac{3n\sqrt{{\Delta}t}}{SNR}$ ($n$ is the number of spins and
$\Delta t$ is 1/linewidth of the observed resonance) is 1.4 nmol s$^{1/2}$ of
protons at 600 MHz, slightly better than the value reported for a smaller
detector by Finch et al.~\cite{gream_2016}.

@@

\begin{figure} \centering
\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-180612-HSQCspect.png}
\caption{ $^1$H-$^{13}$C HSQC spectrum of $^{13}$C labeled glucose (left) and
$^1$H-$^{15}$N HSQC of $^{15}$N labeled Ubiquitin (right) both acquired from
2.5$\mu$l sample volume at 14.1 T. Glucose HSQC spectrum was acquired in 12
minutes from a 100 mM sample. Ubiquitin HSQC spectrum was acquired in 400
minutes from a 1 mM sample.} \label{fig:HSQC} \end{figure}
%$
\cbdelete
The probe can also be used to acquire micro magnetic resonance (MR) images using
a Bruker micro-gradient unit. To this effect, the aluminium probe sleeve must be
replaced by an electrically insulating material in order to avoid image
distortions due to eddy currents in the sleeve.\cbstart\
A shorter aluminium tube with 3D printed top part (made from ABS plastic)
to match the probe height was used.\cbend  \fig{fig:tisli} shows MR images
of mouse liver tissue slice immersed in DMEM cell growth medium. The slice was
placed in a microfluidic device with circular sample chamber centred at the
detector location, as shown in \fig{fig:tisli}(A). The image shown in
\fig{fig:tisli}(B) was acquired using a FLASH pulse sequence with; the lateral dimensions of all MR images in \fig{fig:tisli} are 512$\times$512 pixels at a resolution of 30~$\mu$m. \fig{fig:tisli}(C) shows a
RARE image using the same parameters. A spin echo image is shown in
\fig{fig:tisli}(D). Finally, \fig{fig:tisli}(E) shows a
$B_0$ field map, which has been obtained by acquiring two separate FLASH images.

>>>>

\documentclass[preprint,5p]{elsarticle}
\usepackage{graphicx,amssymb,amsmath,amstext,hyperref,graphics,float,eurosym,geometry,lineno,changebar}
%\linenumbers
\nochangebars
\biboptions{sort&compress}
\hypersetup{
    colorlinks=true,        % false: boxed links; true: colored links
    linkcolor=black,         % color of internal links (change box color with linkbordercolor)    https://www.sharelatex.com/learn/Hyperlinks
    citecolor=black,        % color of links to bibliography
    filecolor=black,      % color of file links
    urlcolor=black           % color of external links
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In this paper we present a novel modular probe designed for generic
microfluidic NMR experiments. The design is based on a transmission line
detector~\cite{stripline_jan,gream_2016} using inexpensive
printed circuit board (PCB) technology. A modular design ensures that detectors of
different geometry and size can be easily exchanged.
The NMR detector (including the tuning and matching circuit) is connected to the probe
skeleton through detachable connectors. Modularity of the probe not only allows
fast optimisation of the detector but also facilitates the use of dedicated detectors
for different microfluidic devices on a single probe base.
Once the probe base is in place, additional detectors can be manufactured
within 2-3 days for less than $\sim$200 $\geneuro$.
The probe is optimised for proton detected double resonance, with the
second channel tunable to different nuclei such as $^{13}$C, $^{15}$N, or
$^{31}$P. The probe skeleton is made almost entirely from easily obtainable raw materials
such as aluminium profiles of standard size, with only a small number of
custom-machined parts holding the structure together.
Detailed construction drawings and a complete set of CAD files is
available for download at \url{https://github.com/marcel-utz/modular-microfluidic-probe}.
The planar geometry of the detector accommodates exchangeable microfluidic devices
which can be designed freely for specific experimental requirements as long as the
overall shape of the device is maintained. \fig{fig:rf-device-assembly} shows the microfluidic device and the detector with their relative positioning.

In the remainder of this paper, we discuss the probe design in more detail,
and characterise its performance in terms of sensitivity and resolution.
We also demonstrate its application in microfluidic cell culture,
protein NMR spectroscopy, and micro-imaging.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Probe Design}
\label{sec:probe-design}
%Figure showing modular probe concept; example of probe base with several inserts\newline
%\begin{itemize}
%	\item Philosophy: use cheap materials and prefab Al profiles wherever possible
%	\item Hold it together with a small number of precision-machined parts
%	\item Generic probe base design that can accommodate a variety of inserts
%	\item Insert: PCB that accommodates both tuning/matching circuitry for up to two channels and the transmission line probe itself
%	\item Tuning and matching capacitors for each channel are part of the probe base
%	\item Connection using standard coaxial RF connectors (SMP)
%	\item Microfluidic chip design; outline
%	\item Design/explosion drawings
%	\item Circuit design for double resonance
%	\item Transmission line connection between tuning/matching of 1H channel and resonator (Smith chart argument)
%	\item 38 mm bore (Bruker NB) and 45 mm bore (Varian/Agilent NB)
%\end{itemize}
\cbstart\
\begin{figure}
\centering
\includegraphics[width=.8\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-190205-rf-device-assembly.png}
\caption{Drawings of the detector assembly and the microfluidic device (1). A: front view (dimensions in mm); B: exploded view. Spacer (4) ensures the alignment of the sample chamber with the constrictions on the PCB planes. In A, PCB plane 5 is hidden to show the orientation of 1 with respect to PCB plane 3. Thickness of each of the PCB planes is 1.52 mm and the copper layers on the PCBs is 35 $\mu$m. Both the microfluidic device and the spacer are made from PMMA and have thickness of 0.9 mm and 1 mm respectively.}
\label{fig:rf-device-assembly}
\end{figure}
\cbend\
%\begin{figure}
%\centering
%\includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181218-probe.png}
%\caption{The probe with and without sleeve.}
%\label{fig:probe}
%\end{figure}
The probe assembly design is based on readily and easily available materials and parts
with minimal need for customised fabrication.
All mechanical and electronic components are readily available from commercial sources,
with the exception of a small number of precision-machined parts which are used
to hold the assembly together. These can be ordered from commercial prototyping
manufacturers or machined in-house if mechanical workshop facilities are available.

\begin{figure}
\centering
\includegraphics[width=.8\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-Probe-explode.png}
\caption{Exploded view of the probe design (left) and assembled probe (center).
Probe base (blue) and scaffold assembly (green) with TMPCB (brown, 7) provides a
generic mounting point for the NMR detector assembly (red).
A microfluidic device (1) can be inserted from the top of the probe.
The device is held in place by a spacer (4) between the detector planes (3 and 5)
ensuring alignment of the sample chamber with the sensitive area on the PCB planes.
The modular NMR detector is made up of parts 3,4 and, 5 and is
connected to the TMPCB (7) through standard coaxial (SMP) connectors.
The scaffold assembly is made up of aluminium tubes (11), scaffold support disks (9)
and, auxiliary support disks (12).}
\label{fig:probe-explode}
\end{figure}

@@

The scaffold assembly is made up of two hollow aluminium tubes (11) held together with
precision machined parts at both ends (scaffold support disks (9)).\cbstart\ The semi-rigid cables (RG 402, 50~$\Omega$) are  threaded through these hollow aluminium tubes
to reach the detector assembly.\cbend\
Auxiliary support disks (12) provide additional rigidity for the scaffold assembly.
In our case, these were laser cut from 5~mm thick poly(methyl methacrylate) (PMMA) sheets,
but they may also be made by conventional machining.
A tuning and matching PCB (TMPCB, 7) is held in place on the top of the probe skeleton by
the detector support rods (8), with the semi-rigid coaxial cables providing
additional support.
The TMPCB is permanently fixed to the probe base, and serves as attachment point
for the exchangeable detector assembly.\cbstart\ It also provides
trimmer capacitors (6) for secondary tuning and matching of the detector.\cbend\ The detector assembly is connected to the TMPCB through a pair of
low-loss SMP connectors (14 in \fig{fig:ProbePhoto}). \cbstart\ The SMP connector receptacle male pin ($J_3$ and $J_4$ in \fig{fig:circuit}) is soldered on the TMPCB and the SMP connector jack male pin is soldered on the PCB plane 3 ($J_1$ and $J_2$ in \fig{fig:circuit}). The TMPCB and 3 are connected by a coaxial connector SMP plug adapter.\cbend\ While each detector assembly is roughly
tuned and matched with fixed circuit elements soldered onto it,
the adjustable capacitors on the TMPCB are used for
fine tuning and matching
at the magnet through tuning rods (10) which reach all the way to the probe base.

The base, the scaffold assembly and the tuning and matching PCB all have a free circular
axial bore providing access from the bottom of the probe, which can be used for
temperature and environmental control and/or fluidic connections to the sample as
needed. The detector assembly is made up of two PCBs (3 and 5) and a spacer (4) between them.\cbstart\ The spacer is made from a 1 mm thick PMMA sheet.\cbend\ The detector used here is based on a planar transmission line geometry as described elsewhere~\cite{gream_2016,stripline_jan}; other structures such as spiral
coils and Helmholtz pairs are also possible, and can easily be realised on a PCB.
The transmission line detector consists of a pair of copper
planes, each with a constriction at the centre.  This geometry gives rise to an
electromagnetic eigenmode with a strong anti-node of the magnetic field between
the two planes at the site of the constriction. This concentrates the rf field
and the detection sensitivity
onto the sample area.
The shape and size of the copper structures have been chosen such as to produce
an eigenfrequency of this mode around 630~MHz. The PCBs have been designed with
solder points at the back side for chip capacitors; these can be used to tune the
resonance down to the desired proton Larmor frequency (500 or 600~MHz in the present case).
Both the PCBs (3 and 5) also carry circuitry for channel separation and primary
matching of the detector. A copper or brass auxiliary disk (2) holds the PCBs
together at the top, and forms the top end of the probe assembly.
The probe sheath (not shown in~\fig{fig:probe-explode}) is fixed to the auxiliary disk (2)
and the scaffold assembly with screws.
An exchangeable microfluidic device (1) can be inserted from the top of the detector.
Microfluidic devices can be used as passive sample holders, filled before putting them
into the probe,
or the device can be actively perfused and operated in-situ.\cbstart\ The device inlet and outlet are sealed by an optical adhesive film (MicroAmp, AB Applied Biosystems)
when using the device as passive sample holder.\cbend\ The microfluidic device is held in place by the spacer
between the two PCB planes coinciding the sample chamber with the constriction on the
detector. The 45-degree edges of the device outline help with precise and reliable
alignment.
Since the detector assembly is attached to the probe base through SMP
connectors, it can easily be exchanged.
Using standard PCB processes to manufacture the detector provides great flexibility
to optimise detector performance for different applications, including different
microfluidic sample sizes, and different combinations of target nuclei.

\begin{figure}
\centering
\includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-both-detectors.png}
\caption{Dual channel probes with (A) and without (B) modular RF insert (13) for X channel.
O.D. of A is 44.45 mm and B is 38 mm. Circuit elements of X channel are integrated on the
PCB in B making it compact. Detachable SMP connectors (14) are used to
connect the RF insert (13) and the detector assembly.}
\label{fig:ProbePhoto}
\end{figure}
\fig{fig:ProbePhoto} shows two different versions of the probe with and without the RF insert (13)
for the X channel. In (A) the X channel can be tuned to different nuclei by exchanging (13).
However, in (B) the circuitry of the RF insert (13) is integrated on the PCB plane (5),
making the design more compact.
 Probe (A) is compatible with a Varian 600 Premium shielded 14.1 T magnet, with an outer diameter (O.D.) of 44.45 mm including the sheath. Probe (B), with an
O.D. of 38 mm including the sheath, is designed to fit inside a
Bruker narrow bore shim stack.
Probe (B) also fits inside a Bruker micro-imaging gradient unit. Naturally, B can also be used with
wide bore magnets with appropriate spacers to keep the probe centered.

The microfluidic devices were made from inexpensive PMMA sheets by laser cutting and
thermal bonding, as described in detail elsewhere \cite{yilmaz_bonding}.\cbstart\ PMMA was chosen for ease of fabrication, but also due to the close match in magnetic susceptibility with that of water (Table~\ref{tab:susceptibility}).\cbend\
Briefly, the devices consist of a 0.5~mm thick middle layer between a  top and
bottom layer of 0.2~mm thickness each. The sample chamber and fluidic network
are cut into the middle layer. The fluidic network on the device can be designed
freely as long as the overall shape of the device is preserved, and the location
of the sample chamber is maintained. The volume of the sample chamber is 2.5~$\mu$l which can be increased or decreased according to the experimental requirements. \cbstart \fig{fig:device} shows various microfluidic devices.\cbend
\cbstart
\begin{table}[h]
\centering
\caption{Magnetic susceptibility values of some relevant materials.\cite{wapler-2014,schenck-1996}}
\label{tab:susceptibility}
\begin{tabular}{||p{.3\linewidth}|p{.3\linewidth}||}
\hline
Material   & $\chi$/ppm	\\
\hline
PMMA		&-9.054	\\
Copper	&-9.63	\\
FR4	&-3.743		\\
Aluminium	&20.7	\\
Water & -9.02\\
\hline
\end{tabular}
\end{table}
\cbend
\cbstart
\begin{figure}
\centering
\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-devices.png}
\caption{Microfluidic devices for different applications compatible with the current setup.
From left: Devices for perfusion of tissue slice on a chip, peristaltic pumping to induce flow,
hydrogenation on a chip, droplet generator, simple design to fill the sample chamber and,
to grow cells on the device.}
\label{fig:device}
\end{figure}
\cbend

@@

\caption{Circuit diagram of the double resonance probe. The background colour relates the different circuit elements on different PCBs. The back side of the PCB plane 5 and the front side of the PCB plane 3 is shown in horizontal orientation. The front side of the TMPCB 7 is shown in vertical orientation. Trimmer capacitor $C_6$ is placed on the back side of PCB plane 3. The copper layer is shown in brown and the solder pads to place the circuit elements are shown in off-white. An insulating solder mask layer over the copper layer prevents accidental short-circuiting.

@@

\cbstart
\begin{figure} \centering
\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/pcb-fieldmap-colorbar.png}
\caption{B\textsubscript{0} field map of the sample chamber for FR4 (A) and
Rogers RO3035 (B) PCB material acquired at 11.7 T. Both the field maps were constructed from 2
gradient echo images acquired on a chip filled with 130 mM sodium acetate
dissolved in H\textsubscript{2}O through same parameters and pulse sequence.}
\label{fig:field map}
\end{figure}
\cbend
\cbdelete
The RF field at proton frequency shows excellent homogeneity, with a
810$^{\circ}$/90$^{\circ}$ ratio of more than 90\% measured from $^1$H nutation at 600~MHz shown in~\fig{fig:1H-nutation}. The
probe generates 100~kHz nutation frequency from 100~W input power both at
600~MHz and 500~MHz, corresponding to RF field efficiency ($B_{1}/\sqrt{power}$)
of 10 kHz/$\sqrt{W}$. The detector geometry has been optimised for a sample
volume of 5~$\mu$l. It compares reasonably well to the value of 22
kHz/$\sqrt{W}$ that has been reported by Finch et al.~\cite{gream_2016} for
single-frequency detector of half this size at a Larmor frequency of 300~MHz.
For the X channel, 100~W of input power produces nutation frequencies of 6 kHz for
$^{15}$N and 14 kHz for $^{13}$C. No signs of arcing were obseved at this power
level for pulses up to 1~ms duration.

@@

\begin{figure}
\centering
\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/media-180125-005-bigger-font.png}
\caption{Spectrum of culture growth media recorded in 256 scans with water presaturation. The total experimental time was 20 min for 2.5 $\mu$l sample volume.}
\label{fig:media-spec}
\end{figure}
\cbdelete
\fig{fig:lineshape} shows the proton spectrum of sodium acetate. The inset shows an expanded view of the base of the acetate peak. Carbon satellites can be seen well above the noise level. The orange curve
corresponds to a Lorentzian lineshape with full width at half maximum of 3.35
Hz, corresponding to 0.0056 ppm. This is very similar to the resolution reported
by Finch et al. at 300~MHz. While the residual cause of broadening is still
under investigation, we have reason to suspect imperfections in the fabrications
of the PMMA microfluidic devices to play a major role. Efforts to mitigate these
and to achieve more highly resolved proton spectra are currently underway in our
laboratory and will be reported at a later occasion.  The limit of detection
$nLOD_{\omega}=\frac{3n\sqrt{{\Delta}t}}{SNR}$ ($n$ is the number of spins and
$\Delta t$ is 1/linewidth of the observed resonance) is 1.4 nmol s$^{1/2}$ for
protons at 600 MHz, slightly better than the value reported for a smaller
detector by Finch et al.~\cite{gream_2016}.

@@

\begin{figure} \centering
\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-180612-HSQCspect.png}
\caption{ $^1$H-$^{13}$C HSQC spectrum of $^{13}$C labeled glucose (left) and
$^1$H-$^{15}$N HSQC of $^{15}$N labeled Ubiquitin (right) both acquired from
2.5$\mu$l sample volume at 14.1 T. Glucose HSQC spectrum was acquired in 12
minutes from a 100 mM sample. Ubiquitin HSQC spectrum was acquired in 400
minutes from a 1 mM sample.} \label{fig:HSQC} \end{figure}
%$
\cbdelete
The probe can also be used to acquire micro magnetic resonance (MR) images using
a Bruker micro-gradient unit. To this effect, the aluminium probe sleeve must be
replaced by an electrically insulating material in order to avoid image
distortions due to eddy currents in the sleeve.\cbstart\
A shorter aluminium tube with 3D printed top part (made from ABS plastic)
to match the probe height was used.\cbend\ \fig{fig:tisli} shows MR images
of mouse liver tissue slice immersed in DMEM cell growth medium. The slice was
placed in a microfluidic device with circular sample chamber centred at the
detector location, as shown in \fig{fig:tisli}(A). The image shown in
\fig{fig:tisli}(B) was acquired using a FLASH pulse sequence with; the lateral dimensions of all MR images in \fig{fig:tisli} are 512$\times$512 pixels at a resolution of 30~$\mu$m. \fig{fig:tisli}(C) shows a
RARE image using the same parameters. A spin echo image is shown in
\fig{fig:tisli}(D). Finally, \fig{fig:tisli}(E) shows a
$B_0$ field map, which has been obtained by acquiring two separate FLASH images.
